Fast solvers for the high-order FEM simplicial de Rham complex \thanks{Submitted to the editors July XX, 2024. \funding{ PDB and PEF were supported by EPSRC grant EP/W026260/1. } }

### 2024-06-27 paper/paper.tex
Solver diagram

\section{Space decompositions}

@@

>>>>

\section{Design of preconditioners}

@@

\begin{figure}
\footnotesize
\centering
\begin{tikzpicture}[%
 every node/.style={draw=black, thick, anchor=west},
grow via three points={one child at (-0.0,-0.7) and
	two children at (0.0,-0.7) and (0.0,-1.4)},
edge from parent path={(\tikzparentnode.210) |- (\tikzchildnode.west)}]
\node {KSP: Conjugate Gradients}
   child {node {PC: Two-level vertex-star additive Schwarz}
   child {node {$p$-fine: Interior-facet additive decomposition}
      child {node {Interior: point-Jacobi}}
      child {node {Facet: vertex-star patches}}
   }
   child[missing]{}
   child[missing]{}
   child {node {$p$-coarse ($p=1$): Cholesky}
      %child {node {Relaxation: Hiptmair--Jacobi}}
      %child {node {$h$-coarse: Cholesky}}
   }
};
\end{tikzpicture}
\caption{Solver diagram for $\Hgrad$ using the interior-facet decomposition.}
\end{figure}
